### 2025-09-25 paper/sec/evaluation.tex
Better RQ2.

\paragraph{RQ2. How sensitive is the system to misleading or adversarial information?}

Authors may (intentionally or unintentionally) introduce misleading elements into the text. These include
inconsistent use of language, incorrect references to numerical values, or contradictory claims. We ask how
the system responds in such cases: does it fail gracefully, does it default to literal reproduction of the
misleading fragment, or does it attempt to generate a plausible, but incorrect, expression?
Table~\ref{tab:problematic_cases} shows some of cases which are ``problematic'' in this sense; in these cases,
producing a valid expression is likely to be challenging because of ambiguities in the input data or
accompanying natural language.

>>>>

\paragraph{RQ2. Generalisability and Robustness.}

How well do the generated expressions generalise when the underlying data changes, or when the input contains
misleading or ill-specified information? We test whether generated queries continue to produce correct outputs
under a set of hand-generated counterfactual modifications of the dataset, based on expected query results
specific to each test case, and also how counterfactual performance is impacted by the presence of misleading
or adversarial phrasing. able~\ref{tab:problematic_cases} shows some of cases which are ``problematic'' in
this sense; in these cases, producing a valid expression is likely to be challenging because of ambiguities in
the input data or accompanying natural language.
